Paper_analyses

### 2022-02-02 Paper_Analyses_subj_obje_arousal.Rmd
initial stab at the timeseries application

>>>>

# fit pupil response froma arousal slope

table(is.na(db_full4new_stim_screen_pupil_nopract$valence_c))
library(lmerTest)
library(tidyverse)
pupil_arousal_findings$pupil_from_ar_slope_vale <- lmer(pup_basCor ~ (valence_c* arousal_c) +
                                                    Mean_gray_z  +
                                                    (1  | ssid)+
                                                    (0+ arousal_c | ssid),
                                                  REML = FALSE,
                      data = db_full4new_stim_screen_pupil_nopract%>%
                         subset(Group == "NT")%>%
                        subset(pupil_outlier == FALSE)%>%
                        subset(arousal_outler == FALSE))

summary(pupil_arousal_findings$pupil_from_ar_slope_vale)
